### 2018-06-11 Shiva Dissertation/chap4/simulation.tex
Shiva PhD dissertation

%Two simulations were implemented using non-slip contact walls for position control.  The first controls the position of two robots, the second controls the position of $n$ robots.  
\begin{figure*}
\begin{overpic}[width=0.67\columnwidth]{regionMove1.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,  - , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove2.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove3.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{regionMove4.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove5.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{regionMove6.pdf}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{Move1.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted    ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move2.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move3.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted    ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}\\

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
For each the move 1 and 3 are simple translations of both particles and so the reachable sets do not change.
The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
See multimedia attachment for animations of each.
}
\end{figure*}

>>>>

%Two simulations were implemented using non-slip contact walls for position control.  The first controls the position of two robots, the second controls the position of $n$ robots.  
\begin{figure*}
\begin{overpic}[width=0.32\columnwidth]{regionMove1.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,  - , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{regionMove2.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{regionMove3.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}\\

\begin{overpic}[width=0.32\columnwidth]{regionMove4.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{regionMove5.pdf}\put(55.5,26){\begin{turn}{94} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{regionMove6.pdf}\end{overpic}\\

\begin{overpic}[width=0.32\columnwidth]{Move1.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted    ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{Move2.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{Move3.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted    ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}\\

\begin{overpic}[width=0.32\columnwidth]{Move4.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{Move5.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
%For each the move 1 and 3 are simple translations of both particles and so the reachable sets do not change.
%The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
%See multimedia attachment for animations of each.
}
\end{figure*}

### 2018-06-11 Shiva Dissertation/chap4/theory.tex
Shiva PhD dissertation

For some configurations, we can obtain the optimal solution. 
Subsections \ref{subsec:square} and \ref{subsec:circular} provide shortest-path results for two representative workspaces, squares and disks.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Interaction Model}\label{subsec:WallFriction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The system dynamics represent particle swarms in low-Reynolds number environments, where viscosity dominates inertial forces and so velocity is proportional to input force~\cite{Purcell1977}. 
 In this regime, the input force command $\mathbf{u}(t)$ controls the velocity of the particles.  
 If the $i^{\textrm{th}}$ particle has position $\mathbf{x}_i(t)$ and velocity $\dot{\mathbf{x}}_i(t)$,  we assume the following system model:
 \begin{align}\label{eq:swarmDynamicsAndFric} 
\dot{\mathbf{x}}_i(t)
 &=
 \mathbf{u}(t)
 +F \left( \mathbf{x}_i(t), \mathbf{u}(t) \right), ~i \in [1,n].\\
 F(\mathbf{x}_i(t), \mathbf{u}(t)) &= \begin{cases}
  - \mathbf{u}(t) &\begin{matrix} \mathbf{x}_i(t) \in  \textrm{boundary \textbf{and}}\\
\mathbf{N}(\textrm{boundary$_{\mathbf{x}_i(t)}$})\cdot   \mathbf{u}(t) \le 0 \end{matrix}
\textrm{    ,} \\
 0 & \textrm{else}.
 \end{cases}\nonumber
 \end{align}
 Here  $F(\mathbf{x}_i(t), \mathbf{u}(t)) $ is the frictional force provided by the boundary, and
 $\mathbf{N}(\textrm{boundary$_{\mathbf{x}_i(t)}$})$ is the normal to the boundary at position $\mathbf{x}_i(t)$.

@@

 \subsection{Example: Shortest Path in a Square Workspace}\label{subsec:square}
 Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle contact a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final positions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle contacts the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal contact location, as shown in Fig. \ref{fig:reflection}. 
  There are four walls, and four candidate solutions, but some candidate solutions may be invalid because a different boundary is hit before the desired first contact position in move $m_1$ (light grey regions) or  invalid because $m_2$ cannot generate the goal relative spacing (dark grey regions).
 %
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{Reflection.pdf}\end{overpic}
\vspace{-2em}
\caption{\label{fig:reflection}
The shortest three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle.
} \vspace{-1em}
\end{figure}
%

This optimization result was implemented in our previous work using a square workspace \cite{shahrokhi2017algorithms}.
 Fig.~\ref{fig:shapeControlMathematica1} shows solutions from a \emph{Mathematica} implementation in a square workspace for six representative configurations.
\begin{figure*}
\renewcommand{\figwid}{0.4\columnwidth}

{\begin{overpic}[width =\figwid]{story1mov0.pdf}\put(10,10){Start}
\put(10,85){a)}
\put(30,70){$s_1$}
\put(48,88){$g_1$}
\put(65,17){$s_2$}
\put(87,52){$g_2$}
\put(60, 3.9){{\tiny$\updownarrow$}~$\epsilon$}
\end{overpic}
\begin{overpic}[width =\figwid]{story1move.pdf}\put(10,10){Move 1}
\put(110,50){If $(\Delta g- \Delta s) = (0,0)$, only one move is needed}
\put(65, 47){{$\xupdownarrow{1.8cm}$}$L$}
%\put(47, 65){$\xleftrightarrow{1.8cm}$}
\end{overpic}
}\\

@@

\vspace{-0.75em}
{
\begin{overpic}[width =\figwid]{storyWorst1.pdf}\put(60,10){Move 1}
\put(10,85){f)}
\put(15,10){$s_1,g_2$}
\put(65,88){$s_2,g_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst2.pdf}\put(60,10){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst4.pdf}\put(60,10){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst6.pdf}\put(60,10){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst7.pdf}\put(60,10){Move 5}
\put(15, 85){worst-case}\put(15,75){path length}\put(15, 62){$(\sqrt{2}+2)L$}
\end{overpic}
}\\

@@

\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:optimalAlg}: two particle positioning using walls with non-slip contacts. 
Particle start positions are shown by squares, and goal positions by circles.  Dashed lines show the shortest route if particles could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:optimalAlg}.
%Online dmonstration and source code at \cite{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
\vspace{-1em}
}
\end{figure*}

 \subsection{Shortest Path in Unit Disk that Intersects Circumference}\label{subsec:circular}

@@

%  This equation can be simplified to 
% 
% \begin{equation}
%\sqrt{1+s^2-2 s \cos \theta}+  \sqrt{1+e^2-2 e \cos(\beta-\theta)}. 
% \end{equation}
% 
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
{\begin{overpic}[width =\figwid]{shortestpath.pdf}
\end{overpic}
}
\caption{\label{fig:shortestpath}{The shortest path between two points $S$ to $E$ in the unit disk that intersects the circumference. The path length as a function of intersection point, $P= (\cos\theta,\sin\theta)$ is shown at right. See \cite{BeckerShortestPath}.}
%\vspace{-1em}
}
\end{figure}

>>>>

For some configurations, we can obtain the optimal solution. 
Subsections \ref{subsec:square} and \ref{subsec:circular} provide shortest-path results for two representative workspaces, squares and disks.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary interaction model}\label{subsec:WallFriction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The system dynamics represent particle swarms in low-Reynolds number environments, where viscosity dominates inertial forces and so velocity is proportional to input force~\cite{Purcell1977}. 
 In this regime, the input force command $\mathbf{u}(t)$ controls the velocity of the particles.  
 If the $i^{\textrm{th}}$ particle has position $\mathbf{x}_i(t)$ and velocity $\dot{\mathbf{x}}_i(t)$,  we assume the following system model:
 \begin{align}\label{eq:swarmDynamicsAndFric} 
\dot{\mathbf{x}}_i(t)
 &=
 \mathbf{u}(t)
 +F \left( \mathbf{x}_i(t), \mathbf{u}(t) \right), ~i \in [1,n].\\
 F(\mathbf{x}_i(t), \mathbf{u}(t)) &= \begin{cases}
  - \mathbf{u}(t) &\begin{matrix} \mathbf{x}_i(t) \in  \textrm{boundary \textbf{and}}\\
\mathbf{N}(\textrm{boundary$_{\mathbf{x}_i(t)}$})\cdot   \mathbf{u}(t) \le 0 \end{matrix}
\textrm{    ,} \\
 0 & \textrm{else}.
 \end{cases}\nonumber
 \end{align}
 Here  $F(\mathbf{x}_i(t), \mathbf{u}(t)) $ is the frictional force provided by the boundary, and
 $\mathbf{N}(\textrm{boundary$_{\mathbf{x}_i(t)}$})$ is the normal to the boundary at position $\mathbf{x}_i(t)$.

@@

 \subsection{Example: shortest path in a square workspace}\label{subsec:square}
 Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle contact a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final positions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle contacts the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal contact location, as shown in Fig. \ref{fig:reflection}. 
  There are four walls, and four candidate solutions, but some candidate solutions may be invalid because a different boundary is hit before the desired first contact position in move $m_1$ (light grey regions) or  invalid because $m_2$ cannot generate the goal relative spacing (dark grey regions).
 %
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{Reflection.pdf}\end{overpic}
%\vspace{-2em}
\caption{\label{fig:reflection}
The shortest three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle.
} %\vspace{-1em}
\end{figure}
%

This optimization result was implemented in our previous work using a square workspace \cite{shahrokhi2017algorithms}.
 Fig.~\ref{fig:shapeControlMathematica1} shows solutions from a \emph{Mathematica} implementation in a square workspace for six representative configurations.
\begin{figure*}
\renewcommand{\figwid}{0.19\columnwidth}

{\begin{overpic}[width =\figwid]{story1mov0.pdf}\put(10,10){Start}
\put(10,85){a)}
\put(30,70){$s_1$}
\put(48,88){$g_1$}
\put(65,17){$s_2$}
\put(87,52){$g_2$}
\put(60, 3.5){{\tiny$\updownarrow$}~$\epsilon$}
\end{overpic}
\begin{overpic}[width =\figwid]{story1move.pdf}\put(10,10){Move 1}
\put(110,50){If $(\Delta g- \Delta s) = (0,0)$, only one move is needed}
\put(65, 47){{$\xupdownarrow{1.5cm}$}$L$}
%\put(47, 65){$\xleftrightarrow{1.8cm}$}
\end{overpic}
}\\

@@

\vspace{-0.75em}
{
\begin{overpic}[width =\figwid]{storyWorst1.pdf}\put(55,10){Move 1}
\put(10,85){f)}
\put(15,10){$s_1,g_2$}
\put(65,88){$s_2,g_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst2.pdf}\put(55,10){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst4.pdf}\put(55,10){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst6.pdf}\put(55,10){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst7.pdf}\put(55,10){Move 5}
\put(15, 85){worst-case}\put(15,75){path length}\put(15, 62){$(\sqrt{2}+2)L$}
\end{overpic}
}\\

@@

\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:optimalAlg}: two particle positioning using walls with non-slip contacts. 
%Particle start positions are shown by squares, and goal positions by circles.  Dashed lines show the shortest route if particles could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:optimalAlg}.
%Online dmonstration and source code at \cite{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
\vspace{-1em}
}
\end{figure*}

 \subsection{Shortest path in unit disk that intersects circumference}\label{subsec:circular}

@@

%  This equation can be simplified to 
% 
% \begin{equation}
%\sqrt{1+s^2-2 s \cos \theta}+  \sqrt{1+e^2-2 e \cos(\beta-\theta)}. 
% \end{equation}
% 
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
{\begin{overpic}[width =\figwid]{shortestpath.pdf}
\end{overpic}
}
\caption{\label{fig:shortestpath}{The shortest path between two points $S$ to $E$ in the unit disk that intersects the circumference. The path length as a function of intersection point, $P= (\cos\theta,\sin\theta)$ is shown at right. %See \cite{BeckerShortestPath}.
}
%\vspace{-1em}
}
\end{figure}

### 2018-06-11 Shiva Dissertation/chap4/theory2robAlgs.tex
Shiva PhD dissertation

\section{Position Control of Two Particles Using Boundary Interaction}\label{sec:PostionControl2Robots}

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{$\Delta$ Configuration Space}
The configuration space for two particles is a four dimensional manifold. Translating both particles the same amount is a trivial operation, but changing the relative positions requires boundary interaction. For this reason, our algorithms use the two dimensional $\Delta$ configuration space.
The $\Delta$ configuration space is a set of all possible $\Delta p$ values, defined as the difference in position of the first particle from the second particle: $\Delta p = p_2 - p_1$.
We use the $\Delta$ configuration space to plan move sequences that achieve the desired relative spacing.  Once the particles have the correct relative spacing, they can be delivered to the goal configuration in one move.

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{Two Particle Path Planning}

@@

\subsection{Convex Polygonal Workspaces: 2-Move Reachable Set}
   \begin{figure}
\centering
\renewcommand{\figwid}{0.8\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,100){Workspace}\put(20,100){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{2-move reachable sets}, are drawn with transparent blue polygons. A polygon with $n$ sides has $n$ 2-move reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the 2-move reachable sets, we can achieve the required relative position in two moves. If $\Delta g$ is not in the 2-move reachable set, we define a temporary goal $\Delta g_c$ (the closest point on the 2-move reachable set to $\Delta g$) and apply two moves to achieve $\Delta g_c$. We repeat this process until the relative goal position is achieved.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
\vspace{-1em}
}
\end{figure}

@@

\begin{figure}
\centering
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{DeltaConfigSquare.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 contacts the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(middle) Similarly, if particle 2 contacts the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
(right) The 2-move reachable sets in the $\Delta$ configuration space is shown.
}
\end{figure}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(12,-3){\small{Case 1: $s_1$ does not contact boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(20,-3){\small{Case 2: $s_1$ contacts boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} highlights the construction of the 2-move reachable sets for a square workspace. There are four 2-move reachable sets, but the horizontal (and vertical) reachable sets are equivalent in the $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle contacts edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always contact before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\subsection{Circular Workspaces: 2-Move Reachable Set}

@@

\subsection{3D workspaces: Cylinders and Prisms}

>>>>

\section{Position control of two particles using boundary interaction}\label{sec:PostionControl2Robots}

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{$\Delta$ configuration space}
The configuration space for two particles is a four dimensional manifold. Translating both particles the same amount is a trivial operation, but changing the relative positions requires boundary interaction. For this reason, our algorithms use the two dimensional $\Delta$ configuration space.
The $\Delta$ configuration space is a set of all possible $\Delta p$ values, defined as the difference in position of the first particle from the second particle: $\Delta p = p_2 - p_1$.
We use the $\Delta$ configuration space to plan move sequences that achieve the desired relative spacing.  Once the particles have the correct relative spacing, they can be delivered to the goal configuration in one move.

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{Two particle path planning}

@@

\subsection{Convex polygonal workspaces: 2-move reachable set}
   \begin{figure}
\centering
\renewcommand{\figwid}{0.48\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,100){Workspace}\put(20,100){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{2-move reachable sets}, are drawn with transparent blue polygons. %A polygon with $n$ sides has $n$ 2-move reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the 2-move reachable sets, we can achieve the required relative position in two moves. If $\Delta g$ is not in the 2-move reachable set, we define a temporary goal $\Delta g_c$ (the closest point on the 2-move reachable set to $\Delta g$) and apply two moves to achieve $\Delta g_c$. We repeat this process until the relative goal position is achieved.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
%\vspace{-1em}
}
\end{figure}

@@

\begin{figure}
\centering
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{DeltaConfigSquare.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
%Boundary interaction is used to change the relative positions of the particles. %Each particle gets the same control input. 
(left and middle) If particle 2 contacts the bottom or right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
%(middle) Similarly, if particle 2 contacts the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
(right) The 2-move reachable sets in the $\Delta$ configuration space is shown.
}
\end{figure}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(12,-3){\small{Case 1: $s_1$ does not contact boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(20,-3){\small{Case 2: $s_1$ contacts boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\vspace{2em}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
%\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} highlights the construction of the 2-move reachable sets for a square workspace. There are four 2-move reachable sets, but the horizontal (and vertical) reachable sets are equivalent in the $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle contacts edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always contact before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\subsection{Circular workspaces: 2-move reachable set}

@@

\subsection{3D workspaces: cylinders and prisms}
